Adopting agile software development in the large organizations: A systematic literature review

### 2014-08-09 journal/content.tex
Renaming content file

-- What can be learned from this`?

--> Motivation for research
-- There are no systematic reviews for this
-- A collection of experience reports can be used for creating a theoretical
   base.
--> There is interest in large scale [ref XP13 workshop]

@@

% ---------------------------------------------------------------------
\section{Background}
\label{sec:background}

Lindvall, M., et al., "Agile Software Development in Large Organizations,"
IEEE Computer, vol. 37, pp. 26-34, 2004.

Boehm, B. and Turner, R., Balancing Agility and Discipline: A Guide for the
Perplexed: Addison-Wesley, 2003.
Boehm, B., "Get ready for agile methods, with care," IEEE Computer, vol. 35,
pp. 64 - 69, 2002.
--> Any hints on size?? Maybe size leaning towards discipline?

What is agile?
[6] Conboy K., Fitzgerald B., “Toward a conceptual framework for agile methods:
a study of agility in different disciplines,”
Proc. ACM workshop on Interdisciplinary software engineering research (WISER), 2004, pp. 37-44.

\subsection{Large scale general references from primary studies}

@@

\subsection{Things that may need to be explained}

>>>>

-- What can be learned from this?

--> Motivation for research
-- There are no systematic reviews for this
-- A collection of experience reports can be used for creating a theoretical
   base.
--> There is interest in large scale [ref XP13 workshop] \cite{Dingsoyr2013a}

@@

Boehm, B. and Turner, R., Balancing Agility and Discipline: A Guide for the
Perplexed: Addison-Wesley, 2003.
Boehm, B., "Get ready for agile methods, with care," IEEE Computer, vol. 35,
pp. 64 - 69, 2002.
--> Size requires more discipline?

\section{Background}
\label{sec:background}

\subsection{Agile software development}

Agile software development is a collection of methods developed as an alternative
to so called traditional development methods. From the point of view of agile
methods traditional methods strive to minimize change during the development
process and attempt to fully define requirements before development. However,
adaptability during the development life cycle and the ability to respond to
conditions unforeseen at start are critical factors for the success of a
software development project. Embracing change during development, people
centricity are, and pursuing high quality from the start are fundamental themes
in agile development.
\cite{Highsmith2001,Cockburn2001}

Agile methods have been both criticized and advocated, and research has shown
that accommodating change may be a factor in both success and failure
\cite{Boehm2002}. It has been shown that agile methods have improved
satisfaction of both customers and developers, but on the other hand there is
evidence that agile methods may not suite well for large undertakings
\cite{Dyba2009}. As a solution \citet{Boehm2002} has suggested that each
organization should find its own balance of agile and plan driven methods.

Two of the most popular agile methods at the time being are Extreme Programming
(XP) and Scrum \cite{Hamed2013}. Scrum is a method which focuses on the project
management viewpoint of agile development \cite{Schwaber2002}. The Scrum method
focuses on time-boxing, continuous tracking of project progress, and customer
centricity. A prominent feature of Scrum is dividing work into sprints, which
are time boxes of 1 to 4 weeks, aimed for producing a finished increment of
working software \cite{Schwaber2002}. The XP development method is a collection
of practices for enabling efficient incremental development \cite{Beck1999}.
Some of the key practices of XP are continuous feedback on development, test
driven development, close customer involvement, pair programming, and continuous
integration (CI) \cite{Beck1999}.

A methodology relating to and complementing agile development is lean software
development. Similarly to Scrum and XP, lean software development aims to
concentrate focus on activities that provide the most value to the customer.
Core principles of lean software development are optimizing the whole, removal
of waste, building quality in, and continuous learning. \cite{Poppendieck2012}

% What is agile?
% [6] Conboy K., Fitzgerald B., “Toward a conceptual framework for agile methods:
% a study of agility in different disciplines,”
% Proc. ACM workshop on Interdisciplinary software engineering research (WISER), 2004, pp. 37-44.

\subsection{Large scale agile development}

@@

\subsection{Adopting agile methods in large organizations}

Introducing agile methods in large organizations is more difficult than it is in
small organizations \cite{Dyba2008}. The difficulty is partly related to size
bringing higher organizational inertia which slows down organizational change
\cite{Livermore2008}. Agile development is not founded on the use of individual
tools or practices, but rather on a holistic way of thinking. Adopting agile
often requires change of the entire organizational culture \cite{Misra2010}.

One significant difference between small and large scale adoptions is that large
organizations have more dependencies between projects and teams. This increases
the need for formal documentation and thus reduces agility \cite{Lindvall2004}.
In addition to inter-team coordination development teams must interact with
other organizational units, which are often non-agile in nature. For instance,
HR may demand individuals to have strictly specified roles in projects
\cite{Boehm2005}, or a change control board may inhibit the use of continuous
integration or refactoring \cite{Lindvall2004}. All units affected by the agile
transformation need to be informed and consulted, and the agile process must be
adjusted according to their needs \cite{Lindvall2004, Cohn2003, Boehm2005}.

Agile methods will also affect management and business related functions. A key
challenge is that management must move away from life-cycle models and towards
iterative and feature centric models \cite{Nerur2005}. The focus must be shifted
from a large scale scope to shorter term project planning \cite{Misra2010}, as
agile methods emphasize that planning is only meaningful for the near future
\cite{Cohn2003}. However, the lack of planning can be a concern as business and
customer relationships often build on long term roadmapping. Enabling operation
with shorter term planning requires educating stakeholders and reviewing
contracting practices \cite{Boehm2005}.

% \subsection{Challenges in adopting agile methods}
%

% \subsection{Success factors in adopting agile methods}
%

\subsection{Summary of things that may need to be explained}
